\documentclass[]{junhu_resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.28\textwidth} 
\namesection{Jun}{Hu}
\end{minipage}
\hfill
\begin{minipage}[t]{0.68\textwidth} 
\infosection{ \urlstyle{same}
\href{http://www.hu-jun.com}{hu-jun.com} | jun.hu@columbia.edu | (646) 271-1419
}
\end{minipage}

\sepsection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.28\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Columbia University}
\descript{M.S. in Computer Science}
\location{Jan 2017 - May 2018}
\location{New York, NY}
\sectionsep

\subsection{Tsinghua University}
\descript{Ph.D. in Biomedicine}
\location{Sep 2006 - Jan 2012}
\location{Beijing, China}
\sectionsep

\subsection{Wuhan University}
\descript{B.S. in Biomedicine}
\location{Sep 2002 - Jul 2006}
\location{Wuhan, China}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     STATUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Status} 
%Permanent Resident via EB-1A (Alien of Extraordinary Ability) in 2015.\\
Permanent Resident\\
Relocating Acceptable
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Databases\\
Advanced Database Systems\\
Big Data Analytics\\
Advanced Big Data Analytics\\
Machine Learning\\
Artificial Intelligence\\
Analysis Of Algorithms\\
Computational Graphics\\
Microservice/Cloud Apps\\
Natural Language Processing
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
Research Papers: \textbf{49}\\
Citations: $>$ \textbf{700} times\\
Full list: \href{https://scholar.google.com/citations?user=Vr8dYJsAAAAJ}{bit.ly/2xVZYic}
\sectionsep
%[1]. Xie C\textbf{*}, \textbf{Hu J*}, Motloch LJ, Karam BS, \& Akar FG. (2015). \textit{J Am Coll Cardiol}., 66(10), 1144-1156. (*Equal, IF=19.896, $1^{st}$ in cardiology)

%2]. \textbf{Hu J}, et.al. (2012). \textit{Eur J Pharmacol}, 674(2-3), 132-142.

%[3]. \textbf{Hu J}, et.al. (2012). \textit{Afr J Pharm Pharmacol}, 6(14), 1069-1076.

%[4]. \textbf{Hu J}, et.al. (2011). \textit{Food Chem Toxicol}, 49(6), 1455-1463.

%[5]. \textbf{Hu J}, et.al. (2010). \textit{Tsinghua Sci Technol}, 15(4), 452-459.

%[6]. \textbf{Hu J}, et.al. (2008). \textit{Tsinghua Sci Technol}, 13(4), 474-479.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
%\subsection{Programming}
\location{
Java \textbullet{} Python \textbullet{} Shell  \textbullet{} R
}
%\sectionsep
\location{Docker \textbullet{} Elasticsearch \textbullet{} Kafka}
%\sectionsep
%\subsection{Database:}
\location{Graph Database \textbullet{} SQL \textbullet{} Hive
%\location{PostgreSQL \textbullet{} SQLAlchemy\\
%Spark SQL \textbullet{}  HBase \textbullet{} Hive\\
%DynamoDB
}
%\sectionsep
%\subsection{Web Develop}
\location{
HTML \textbullet{} CSS \textbullet{} Sass \textbullet{} Javascript
%Node.js \textbullet{} Express \textbullet{} Serverless 
}
%\sectionsep
%\subsection{Machine Learning}
\location{
TensorFlow \textbullet{} Scikit-learn
%Numpy \textbullet{} SciPy \textbullet{} Pandas\\
%Scikit-learn \textbullet{} NLTK  \textbullet{} ggplot2\\
%Spark MLlib
}
%\sectionsep
%\subsection{Others}
\location{
Git  \textbullet{} \LaTeX}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Portfolio: \href{http://www.hu-jun.com}{hu-jun.com}\\
Linkedin: \href{https://www.linkedin.com/in/jun-hu-664639a2/}{/jun-hu-664639a2} \\
Scholar: \href{https://scholar.google.com/citations?user=Vr8dYJsAAAAJ&hl=en}{bit.ly/2xVZYic}\\
Github: \href{https://github.com/vibrioh}{/vibrioh}\\
Facebook: \href{https://www.facebook.com/hjun1}{/hjun1}\\
Twitter: \href{https://twitter.com/vibrioh1}{/vibrioh1}\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.68\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Graphen, Inc} \hspace*{0pt}\hfill  \location{New York, NY}
\descript{Principal Research Scientist, Big Data \hspace*{0pt}\hfill \location{Sep 2018 –– Current}}
\descript{Research Scientist \hspace*{0pt}\hfill \location{Jan 2018 – Sep 2018}}
\location{Delivered 1 FinTech project (\SI{10}[\$]{M}) as a DevOps engineer on-site.}
\location{Delivering 1 Cybersecurity project (\SI{0.8}[\$]{M}) as a data scientist.}
\location{Delivered 1 HealthCare project (non-profit with Harvard).}
\location{Implemented Client Module of the Graph Database.}
\location{Implemented Integration and Automation of Ardi Platform}
\location{Accomplished Business Logic and Educated Customers.}
\smallsep
\sectionsep

\runsubsection{Icahn School of Medicine at Mount Sinai} \hspace*{0pt}\hfill  \location{New York, NY}
%Icahn School of Medicine at Mount Sinai
\descript{Postdoctoral Fellow \hspace*{0pt}\hfill \location{Apr 2012 - Dec 2016}}
\location{Automated Optical-Mapping Data Transformation.}
\location{Developed Pipeline of Large-Scale Sequencing Analysis.}
\sectionsep

%\runsubsection{Tsinghua University}
%Beijing, China\\
%\descript{Research Assistant | Sep 2006 – Jan 2012}
%\location{$\vdash$Published 20+ research papers and oversaw lab members.}
%\smallsep
%\descript{Undergraduate Advisor | Sep 2007 – Feb 2010}
%\location{$\vdash$Academically advised undergraduates and managed scholarship.}
%\smallsep
%\descript{Olympic Media Village Volunteer | July 2008 – Aug 2008}
%\location{$\vdash$Led a hotel team of 70 volunteers and was certificated by 5-star hotel.}
%\smallsep
%\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\location{Learn More: \href{http://hu-jun.com/projects.html}{hu-jun.com/projects.html}}
\sectionsep
\runsubsection{ICBC Non-Performing Loans Prediction}\\
\descript{Industrial and Commercial Bank of China (ICBC), the largest bank in the world, requests IBM an AI solutions (\SI{10}[\$]{M})
	to predict non-performing loans, simulate loan default cascades by user modifying relations/properties, 
	find hidden relationships and display dynamic network evaluation.
	Graphen, inc provides high-performance distributed graph database
	solutions (\SI{2}[\$]{M}).}
    \descript{$\Longrightarrow$ I am in charge of the system integration (Shell/Python scripts), the REST/Client and
	Dynamic Graph backend (Java/Spring). The containers of Grest/Gasync (Flask/uWSGI/Nginx/Ubuntu, Docker) 
	are deployed with clustered Kafka and running on openSUSE servers. Upstream ETL processes data from ICBC Data Warehouse
	daily, triggering High Availability Module, which is monitoring server
	health status, switching between available servers and executing requests. 
	After loading through Async/Kafka, the predefined analytics scripts (business logic) compute all the features
	needed for UI and ML module, such as guarantee cycles, closeness, betweenness, page rank and so on. 
	The results are both stored locally in graph database and ported to Oracle Database.}
\sectionsep

\runsubsection{BOC Adaptive Cybersecurity Monitoring}\\
\location{Bank of China New York Branch Smart-i (\SI{0.8}[\$]{M}). The system shall gather all relevant and available information about users,
	devices, applications, and network events, detect anomalies at various
	levels, and provide an aggregate risk assessment to predict cybersecurity risks. }
\location{$\Longrightarrow$ I am in charge of feature selection and graph database.}
\sectionsep

\runsubsection{Cancer Classification}
\location{N-Grams in Amino Acids Sequence.}
\runsubsection{Real Estate Management}
\location{PostgreSQL, FLASK and Bootstrap.}

\runsubsection{Natural Language Processing}
\location{POS, PCFG and HMM.}

\runsubsection{Wind Prediction}
\location{TensorFlow, GPU, LSTM and RNN.}

\runsubsection{Query Expansion}
\location{Google Search API and Rocchio Algorithm.}
\runsubsection{Iterative Set Expansion}
\location{Google Cloud and NLPcore.}

\runsubsection{Movie Search Engine}
\location{Elasticsearch and Full-text Search.}


\runsubsection{Arrhythmia Visualization}
\location{R, OriginLab and Mathematics.}

\runsubsection{Large-Scale Sequencing}
\location{Super Computer and Bioinformatics.}

\runsubsection{3D Graphics and Animation}
\location{Java, OpenGL and LWJGL.}

%\runsubsection{Real Estate Management}
%\descript{Repository \href{http://bit.ly/2jh9Al9}{http://bit.ly/2jh9Al9}}
%\location{The website was designed for buyers to search and purchase, agents to register/login and list real estate properties, and the administrator to manage all the properties information. The application was achieved with Python/Flask , PostgreSQL/SQLAlchemy, and HTML5/CSS3/JavaScript. The website was tested successfully on Google Cloud.}
%\sectionsep

%\runsubsection{Arrhythmia Visualization}
%\descript{Video Demo \href{http://bit.ly/2wRjr6z}{http://bit.ly/2wRjr6z}}
%\location{As seen in the video, the signal captured by voltage-sensitive dyes can be recorded as  a series of 100$\times$100 matrices, up to 10,000 frames/s. Besides the regular %analysis method, I developed a novel way using R/ggplot2 to calculate and display action potential duration alternans.}
%\sectionsep

%\runsubsection{Large-scale Sequencing}
%\descript{Repository \href{http://bit.ly/2xgFR0O}{http://bit.ly/2xgFR0O}}
%\location{Began with data retrieval, storage and transformation, Chip-seq and RNA-seq analysis was involved 20+ bioinformatics packages. Due to the huge amount computing %load, the mapping was achieved on the remote supercomputer. The visualization was built by R in local system.}
%\sectionsep






\end{minipage} 
\end{document}  \documentclass[]{article}
